Use of management strategy evaluation to inform in fisheries management in a changing climate

### 2019-08-28 Poster_ICES.Rmd
Remove footer; remove title for now; wrangle data for tables; add driver plot; add tables

---
main_topsize: 0.2 #percent coverage of the poster
main_bottomsize: 0.1
#ESSENTIALS
author:
  - name: '**Jonathan W. Cummings**'
    affil: 1
    main: true
    orcid: '0000-0001-8028-5787'
    twitter: jonwcummings 
    email: 'jcummings@umassd.edu'
  - name: Amanda Hart
    affil: 1
    main: true
    orcid: '0000-0002-6449-9328'
    email: 'ahart2@umassd.edu'
  - name: Gavin Fay
    main: true
    affil: 1
    email: 'gfay@umassd.edu'
affiliation:
  - num: 1
    address: School for Marine Science and Technology, University of Massachusetts - Dartmouth 836 South Rodney French Blvd,New Bedford, MA, USA 02744
main_findings:
  - "Make **better posters** with RMarkdown + **posterdown**.
  Use of management strategy evaluation to inform in fisheries management in a changing climate"
logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logocenter_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/qr-code-black.png
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: packages.bib
link-citations: true
---
```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html")
##### load libraries #####
library(tidyverse) # upgrade to base R
library(readxl) # read in excel files
library(shiny) # Shiny App
library(shinythemes) # web themes for Shiny
library(DT) # Data Table
library(purrr) # for loop alternative
library(ggmap) # map plotting
library(mapdata) # basemap generation
library(odbc) # database connection 
library(RMySQL) # MySQL scripting in R
library(DBI) # database interface
library(kableExtra) # extra formating of the tables

@@

# label MSEs articles by analysis for ploting
freq.data_pub<-mutate(freq.data_pub,Analysis="Reviewed")
freq.data_CC<-mutate(freq.data_CC,Analysis="Climate Change")
freq.data<-rbind(freq.data_pub,freq.data_CC)
part.data_pub<-mutate(part.data_pub,Analysis="Reviewed")
part.data_CC<-mutate(part.data_CC,Analysis="Climate Change")
part.data<-rbind(part.data_pub,part.data_CC) %>% 
  arrange(Stage, Percent) %>% 
  mutate(order = row_number())
part.data$order<-c(1,2,3,3,4,4,5,6,7,8,6,9,10,8,9,11,12,10,13,12,13,14,14,15,16,17,18,19,20,
                   16,17,18,20,21,22,23,24,25,21,23,26,25,26,27,27,28,29,30,31,29,32,30,33,
                   32,33,34,35,36,37,38,39,39)
drive.data_pub<-mutate(drive.data_pub,Analysis="Reviewed") %>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,Driver,Percent,Frequency)
drive.data_CC<-mutate(drive.data_CC,Analysis="Climate Change")%>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,Driver,Percent,Frequency)
drive.data<-rbind(drive.data_pub,drive.data_CC) %>% 
  select(Analysis,Driver,Percent,Frequency) %>% 
  arrange(desc(Percent),Driver)

@@

as_tibble(summary.data_pub)
as_tibble(summary.data_CC)
```
---
title: Use of management strategy evaluation to inform in fisheries management in a changing climate
---

# Introduction
For most of its history fisheries management has prodominately focused on fishing impacts with ecosystem status viewed as a background constant. The increasing rate and degree of ecosystem climatic change is changing this dynamic, bringing ecosystem status to the forefront of fisheries management.

@@

Score the MSE documentation:  
Steps  
Problem  
Objectives  
Alternatives  
Consequences  
Trade-offs  
Decision  
Participants  
Roles

@@

```{r, mapfigure, fig.cap='Here is a caption for the figure. This can be added by using the "fig.cap" option in the r code chunk options, see this [link](https://yihui.name/knitr/options/#plots) from the legend himself, [Yihui Xie](https://twitter.com/xieyihui).', out.width="100%"}
MSE.map
```

Figure \@ref(fig:explicit)!

@@

Figure \@ref(fig:participants)!

@@

The drivers modeled in the reviewed MSEs Table \@ref(tab:driversPub) and the climate change MSEs Table \@ref(tab:driversCC) [description of results].

```{r, drivers}
color_Pub <- which(drive.data$Analysis=='Reviewed')
color_CC <- which(drive.data$Analysis=='Climate Change')

drive.data %>% 
  kable(align = "c") %>%
  row_spec(color_CC, color = "#FF0033", background = "white") %>% 
  row_spec(color_Pub, color = "#0000FF", background = "white")

knitr::kable(
  as_tibble(drive.data), format = "html",
  caption = "Drivers modeled in management strategy evaluations",
  align = "c", escape = FALSE)
```

```{r, iristable}
knitr::kable(
  iris[1:15,1:5], format = "html",
  caption = "A table made with the **knitr::kable** function.",
  align = "c", col.names = c("Sepal <br> Length",
                             "Sepal <br> Width",
                             "Petal <br> Length",
                             "Petal <br> Width",
                             "Species"),
  escape = FALSE)
```

>>>>

---
main_topsize: 0.2 #percent coverage of the poster
main_bottomsize: 0
#ESSENTIALS
title:
author:
  - name: '**Jonathan W. Cummings**'
    affil: 1
    main: true
    orcid: '0000-0001-8028-5787'
    twitter: jonwcummings 
    email: 'jcummings@umassd.edu'
  - name: Amanda Hart
    affil: 1
    main: true
    orcid: '0000-0002-6449-9328'
    email: 'ahart2@umassd.edu'
  - name: Gavin Fay
    main: true
    affil: 1
    email: 'gfay@umassd.edu'
affiliation:
  - num: 1
    address: School for Marine Science and Technology, University of Massachusetts - Dartmouth 836 South Rodney French Blvd,New Bedford, MA, USA 02744
main_findings:
  - "Make **better posters** with RMarkdown + **posterdown**.
  Use of management strategy evaluation to inform in fisheries management in a changing climate"
logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logocenter_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/qr-code-black.png
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: packages.bib
link-citations: true
---
```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html")
##### load libraries #####
library(tidyverse) # upgrade to base R
library(readxl) # read in excel files
library(shiny) # Shiny App
library(shinythemes) # web themes for Shiny
library(DT) # Data Table
library(purrr) # for loop alternative
library(ggmap) # map plotting
library(mapdata) # basemap generation
library(odbc) # database connection 
library(RMySQL) # MySQL scripting in R
library(DBI) # database interface
library(kableExtra) # extra formating of the tables

@@

# label MSEs articles by analysis for ploting
freq.data_pub<-mutate(freq.data_pub,Analysis="Reviewed")
freq.data_CC<-mutate(freq.data_CC,Analysis="Climate Change")
freq.data<-rbind(freq.data_pub,freq.data_CC)
part.data_pub<-mutate(part.data_pub,Analysis="Reviewed")
part.data_CC<-mutate(part.data_CC,Analysis="Climate Change")
part.data<-rbind(part.data_pub,part.data_CC) %>% 
  arrange(Stage, Percent) %>% 
  mutate(order = row_number())
part.data$order<-c(1,2,3,3,4,4,5,6,7,8,6,9,10,8,9,11,12,10,13,12,13,14,14,15,16,17,18,19,20,
                   16,17,18,20,21,22,23,24,25,21,23,26,25,26,27,27,28,29,30,31,29,32,30,33,
                   32,33,34,35,36,37,38,39,39)
drive.data_pub<-mutate(drive.data_pub,Analysis="Reviewed") %>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,Driver,Percent,Frequency)
drive.data_CC<-mutate(drive.data_CC,Analysis="Climate Change")%>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,Driver,Percent,Frequency)
drive.data<-rbind(drive.data_pub,drive.data_CC) %>% 
  arrange(Percent) %>%
  mutate(order = row_number())
drive.data$order<-c(6,5,4,3,2,1,8,7,12,9,3,15,14,13,12,11,10,14,16,15,
                   16,6)
# Wrangle objective category data by reviewed, climate change, and combined
objcat.data_pub<-mutate(objcat.data_pub,Analysis="Reviewed") %>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,'Objective Category',Percent,Frequency)
objcat.data_CC<-mutate(objcat.data_CC,Analysis="Climate Change")%>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,'Objective Category',Percent,Frequency)
objcat.data<-rbind(objcat.data_pub,objcat.data_CC) %>% 
  rename(OC='Objective Category') %>% 
  arrange(OC) %>% 
  rename('Objective Category'=OC)

# Wrangle objective data by reviewed, climate change, and combined
obj.dataTable_pub<-mutate(obj.dataTable_pub,Analysis="Reviewed") %>% 
  mutate(Percent=round(Percent,0))
obj.dataTable_CC<-mutate(obj.dataTable_CC,Analysis="Climate Change")%>% 
  mutate(Percent=round(Percent,0))
obj.dataTable<-rbind(obj.dataTable_pub,obj.dataTable_CC) %>% 
  filter(Objective=="Category") %>%
  group_by(Analysis) %>% 
  summarise('AVG'=sum(Number)) %>% 
  mutate(count=c(11,30)) %>% 
  mutate('Per MSE'=round(AVG/count,1)) %>% 
  mutate('Type'=c("Objectives","Objectives"))

altcat.data_pub<-mutate(altcat.data_pub,Analysis="Reviewed") %>% 
  mutate(Percent=round(Percent,0))
altcat.data_CC<-mutate(altcat.data_CC,Analysis="Climate Change")%>% 
  mutate(Percent=round(Percent,0))
altcat.data<-rbind(altcat.data_pub,altcat.data_CC) %>%
  group_by(Analysis) %>% 
  summarise('AVG'=sum(Number)) %>% 
  mutate(count=c(11,30)) %>% 
  mutate('Per MSE'=round(AVG/count,1)) %>% 
  mutate('Type'=c("Alternatives","Alternatives"))

per.MSE<-rbind(obj.dataTable,altcat.data) %>% 
  mutate(order=c(2,1,4,3)) %>% 
  arrange(order) %>% 
  select(Type,Analysis,'Per MSE')

@@

Driver.plot<-ggplot(drive.data,aes(x=order,y=Percent,fill=Analysis)) +
  geom_col(position="dodge") +
  scale_fill_manual(values=c("#FF0033","#0000FF")) +
  scale_x_continuous(breaks = drive.data$order,
                     labels = drive.data$Driver)+
  scale_y_continuous(limits=c(0,100),expand = c(0,0))+
  ylab("Percent")+xlab(NULL)+coord_flip() +
  guides(fill = guide_legend(reverse=T)) + theme_bw() +
  theme(legend.position = c(0.85,0.085),legend.title = element_blank())
```

# Introduction
For most of its history fisheries management has focused on fishing impacts with ecosystem status viewed as a background constant. The increasing rate and degree of climate change is changing this dynamic, bringing ecosystem status to the forefront of fisheries management.

@@

@@

```{r, mapfigure, fig.cap='Map of MSE study locations. Here is a caption for the figure. This can be added by using the "fig.cap" option in the r code chunk options, see this [link](https://yihui.name/knitr/options/#plots) from the legend himself, [Yihui Xie](https://twitter.com/xieyihui).', out.width="100%"}
MSE.map
```

Figure \@ref(fig:explicit)

@@

Figure \@ref(fig:participants)

@@

Figure \@ref(fig:driversPlot)

```{r driversPlot, fig.cap='text', fig.height=6, out.width="100%"}
Driver.plot
```

The categories of objectives considered in MSEs, Table \@ref(tab:objectiveCategories)

```{r, objectiveCategories}
color_Pub <- which(objcat.data$Analysis=='Reviewed')
color_CC <- which(objcat.data$Analysis=='Climate Change')

objcat.data %>%
  kable(align = "c", caption = "Objective categories considered in management strategy evaluations") %>%
  row_spec(color_CC, color = "#FF0033", background = "white") %>%
  row_spec(color_Pub, color = "#0000FF", background = "white")
```

A greater number of objectives were considered per MSE in the random sample of reviewed MSEs than in the climate change MSEs (Table \@ref(tab:PerMSE))

```{r, PerMSE}
color_Pub <- which(per.MSE$Analysis=='Reviewed')
color_CC <- which(per.MSE$Analysis=='Climate Change')

per.MSE %>%
  kable(align = "c", caption = "Objective data reviewed") %>%  
  row_spec(color_CC, color = "#FF0033", background = "white") %>%
  row_spec(color_Pub, color = "#0000FF", background = "white")
```
